### 2020-05-28 README.Rmd
readme

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)
[![Travis build status](https://travis-ci.com/c1au6i0/covid19census.svg?branch=master)](https://travis-ci.com/c1au6i0/covid19census_dev)
[![Codecov test coverage](https://codecov.io/gh/c1au6i0/covid19census/branch/master/graph/badge.svg)](https://codecov.io/gh/c1au6i0/covid19census?branch=master)
<!-- badges: end -->

@@

devtools::install_github("c1au6i0/covid19census_dev", auth_token = "8ca5cd2bb556a45f1ffeb2e9b44c90d4fbef6cf2")
```

>>>>

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)
[![Travis build status](https://travis-ci.com/c1au6i0/covid19census_dev.svg?token=PM6d4w2yt4HVWw7s2Jgy&branch=dev)
[![Codecov test coverage](https://codecov.io/gh/c1au6i0/covid19census/branch/master/graph/badge.svg)](https://codecov.io/gh/c1au6i0/covid19census?branch=master)
<!-- badges: end -->

@@

devtools::install_github("c1au6i0/covid19census_dev", auth_token = "8ca5cd2bb556a45f1ffeb2e9b44c90d4fbef6cf2", ref = "dev")
```
